Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-06-01 Tracked changes/comparison/main_rev.tex
re-render latexdiff

% add reference library file
\addbibresource{../references.bib}

@@

% Abstract
\abstract{
One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and leads to better intergroup relations. We propose to consider the fulfillment of situationally relevant needs during everyday intergroup contact. We conducted three extensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup (total \textit{N} of measurements = 10,297; total \textit{N} participants = 207). The novel need fulfillment mechanism is consistently a strong predictor of perceived interaction quality as well as positive outgroup attitudes following intergroup interactions. The situational needs model is robust to alternative models and works at least as well as Allport's contact conditions. As one of the first studies to test intergroup contact theory using extensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block of understanding and addressing positive intergroup interactions.

>>>>

% add reference library file
\addbibresource{../../references.bib}

@@

% Abstract
\abstract{
One challenge of modern intergroup contact research has been the question of when and why an interaction is perceived as positive and improves intergroup relations. We propose to consider the perceived fulfillment of the situationally most relevant need. We conducted three intensive longitudinal studies with recent migrants, to capture their interactions with the majority outgroup ($N_{measurements}$ = 10,297; $N_{participants}$ = 207). The core need fulfillment mechanism is consistently a strong predictor of perceived interaction quality and positive outgroup attitudes following intergroup interactions. The model is specific to outgroup contact, robust to various need types, and works at least as well as Allport's contact conditions. As one of the first studies to test intergroup contact theory using intensive longitudinal data, we offer insight into the mechanisms of positive intergroup contact during real-life interactions and find situational motivations to be a key building block for understanding and addressing positive intergroup interactions.
